QALY Comparison - Living Wage Intervention

### 2023-11-09 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Added targets for calculating qalys on glasgow synthetic simulation runs
Added diagnostic SF12 plots to QALY comparison scripts, and changed pointer to glasgow_scaled for visualising synthetic population runs

```{r}
# # read in QALY files for baseline and interventions
out.path <- here::here('output', 'default_config')

@@

```{r}
ggplot(data = combined, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
  geom_smooth() +
  labs(title = 'QALYs per year')

# Now change from baseline
combined.QALY.change <- combined %>%
  select(run_id, year, intervention, QALYs) %>%
  pivot_wider(names_from = 'intervention',
              values_from = 'QALYs') %>%
  mutate(QALYs = energyDownlift - energyDownliftNoSupport) %>%
  select(run_id, year, QALYs)

ggplot(data = combined.QALY.change, aes(x = year, y = QALYs)) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  geom_smooth() +
  labs(title = 'QALY change', subtitle = 'Support vs No Support')
```

## Area Under the Curve Comparison

>>>>

```{r}
# # read in QALY files for baseline and interventions
out.path <- here::here('output', 'glasgow_scaled')

@@

```{r}
QALY_comparison(base = noSupport,
                base.name = 'energyDownliftNoSupport',
                int = support,
                int.name = 'energyDownlift')
```

## SF12 Change

```{r}
sf12.plots(base = noSupport,
           base.name = 'energyDownliftNoSupport',
           int = support,
           int.name = 'energyDownlift')
```

## Area Under the Curve

### 2023-11-09 minos/testing/QALY_comparison_livingWage.Rmd
Added diagnostic SF12 plots to QALY comparison scripts, and changed pointer to glasgow_scaled for visualising synthetic population runs

```{r}
ggplot(data = combined, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
  geom_smooth() +
  labs(title = 'QALYs per year')

# Now change from baseline
combined.QALY.change <- combined %>%
  select(run_id, year, intervention, QALYs) %>%
  pivot_wider(names_from = 'intervention',
              values_from = 'QALYs') %>%
  mutate(QALYs = livingWageIntervention - baseline) %>%
  select(run_id, year, QALYs) %>%
  mutate(intervention = 'LivingWage')

ggplot(data = combined.QALY.change, aes(x = year, y = QALYs, group = intervention, colour = intervention)) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  geom_smooth() +
  labs(title = 'QALY change from Baseline')
```

@@

```{r}
# histogram of qalys
ggplot(combined, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  facet_wrap(~year)

ggplot(filter(combined, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'QALYs by run', subtitle = '2022')

ggplot(filter(combined, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'QALYs by run', subtitle = '2028')

ggplot(filter(combined, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'QALYs by run', subtitle = '2034')
```

@@

```{r}
# histogram of qalys
ggplot(combined.QALY.change, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  facet_wrap(~year)

ggplot(filter(combined.QALY.change, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'QALY change by run', subtitle = '2022')

ggplot(filter(combined.QALY.change, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'QALY change by run', subtitle = '2028')

ggplot(filter(combined.QALY.change, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'QALY change by run', subtitle = '2034')
```

@@

```{r}
ggplot(combined, aes(x = year, y = SF_12_MCS, group = intervention, colour = intervention)) +
  geom_smooth()

ggplot(combined, aes(x = SF_12_MCS, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  facet_wrap(~year)

ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention)) +
  geom_smooth()

ggplot(combined, aes(x = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  facet_wrap(~year)
```

>>>>

```{r}
QALY_comparison(base = base,
                base.name = 'baseline',
                int = wage,
                int.name = 'livingWageIntervention')
```

@@

```{r}
# # histogram of qalys
# ggplot(combined, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   facet_wrap(~year)
# 
# ggplot(filter(combined, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'QALYs by run', subtitle = '2022')
# 
# ggplot(filter(combined, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'QALYs by run', subtitle = '2028')
# 
# ggplot(filter(combined, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'QALYs by run', subtitle = '2034')
```

@@

```{r}
# # histogram of qalys
# ggplot(combined.QALY.change, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   facet_wrap(~year)
# 
# ggplot(filter(combined.QALY.change, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'QALY change by run', subtitle = '2022')
# 
# ggplot(filter(combined.QALY.change, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'QALY change by run', subtitle = '2028')
# 
# ggplot(filter(combined.QALY.change, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'QALY change by run', subtitle = '2034')
```

@@

```{r}
# ggplot(combined, aes(x = year, y = SF_12_MCS, group = intervention, colour = intervention)) +
#   geom_smooth()
# 
# ggplot(combined, aes(x = SF_12_MCS, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   facet_wrap(~year)
# 
# ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention)) +
#   geom_smooth()
# 
# ggplot(combined, aes(x = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   facet_wrap(~year)
```

## SF12 Change

```{r}
sf12.plots(base = noSupport,
           base.name = 'energyDownliftNoSupport',
           int = support,
           int.name = 'energyDownlift')
```
